%
% The MIT License (MIT)
%
% Copyright (c) 2016 Paul Batty
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in
% all copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
% THE SOFTWARE.
%

\section{Appendix}
\label{sec:appendix}

\subsection{Appendix A}
\label{subsec:append_a}

Table~\ref{tbl:sqlite_header} show the header layout.  All multibyte fields are stored in a big-endian format.

\begin{longtable}[h]{| c | c | p{10cm} |}
		\hline
			\textbf{Byte Offset} & \textbf{Byte Size} & \textbf{Description} \\ 
		\hline
		\endhead
			0 & 16 & A UTF-8 Header String followed by null terminator read as: "SQLite format 3" or in hex: "53 51 4c 69 74 65 20 66 6f 72 6d 61 74 20 33 00". \\
		\hline
			16 & 2 & Page Size 	in bytes, power of two between 512 - 65536 bytes. if using version 3.7.0.1 and earlier between 512 - 32768, or 1 for 65536. \\
		\hline
			18 & 1 & Write version, 1 for legacy; 2 for WAL. \\
		\hline
			19 & 1 & Read version, 1 for legacy; 2 for WAL. \\
		\hline
			20 & 1 & Bytes of unused space at the end of each page. This space is used by extensions, such as cryptographic to store a checksum, but normally 0. \\
		\hline
			21 & 1 & Maximum embedded payload fraction, must be 64. Was going to be used to determine the maximum size of a B-Tree cell on a index B-Tree. \\
		\hline
			22 & 1 & Minimum embedded payload fraction, must be 32. Was going to be used to determine the portion of a B-Tree cell that has one or more overflow pages on a index B-tree. \\
		\hline
			23 & 1 & Leaf payload fraction, must be 32. Was going to be used to determine the portion of a B-Tree cell that has one or more overflow pages on a leaf or table B-Tree. \\
		\hline
			24 & 4 & File change counter. It counts the number of times the database is unlocked after being modified. May not be incremented in WAL mode. \\
		\hline
			28 & 4 & Size of the database in pages, Total number of pages. \\
		\hline
			32 & 4 & Page number of first freelist page, or 0 if no freelist. \\
		\hline
			36 & 4 & Number of freelist pages. \\
		\hline
			40 & 4 & Schema Cookie. The schema version, each time the schema is modified this number is incremented. \\
		\hline
			44 & 4 & Schema format number. either 1, 2, 3 or 4. \newline
			1. Format support back to version 3.0.0. \newline
			2. Varying number of columns within the same table. From Version 3.1.3. \newline 
			3. Extra column can be non-NULL values. From Version 3.1.4. \newline
			4. Respects DESC keyword and boolean type. From Version 3.3.0. \newline \\
		\hline
			48 & 4 & Page cache size. suggestion only towards Sqlite's pager. \\
		\hline
			52 & 4 & Page number of largest root B-Tree, when in vacuum mode else 0. \\
		\hline
			56 & 4 & Text encoding. \newline
			 1 for UTF-8. \newline 
			 2 for UTF-816le. \newline 
			 3 for UTF-816be. \\
		\hline
			60 & 4 & User version. Set by and read by the user, not used by Sqlite. \\
		\hline
			64 & 4 & Incremental-vacuum mode. Non 0 for true. 0 for false \\
		\hline
			68 & 4 & Application ID. Used to associate the database with a application. 0 is Sqlite3 Database \\
		\hline
			72 & 20 & Empty, Reserved for expansion. \\
		\hline
			92 & 4 & Version-valid-for-number. Value of the change counter when the Sqlite version number was stored. \\
		\hline
			96 & 4 & Version. Sqlite version. \\
		\hline
	\caption{Sqlite Header, modified from \cite{sqlite}}
	\label{tbl:sqlite_header}
\end{longtable}

\subsection{Appendix B}
\label{subsec:append_b}

Time in milliseconds to parse a database.

\begin{longtable}[h]{| c |}
		\hline
			\textbf{Time in milliseconds} \\ 
		\hline
		\endhead
 		210 \\
 				\hline
		147 \\
				\hline
		147 \\
				\hline
		163 \\
				\hline
		145 \\
				\hline
		142 \\
				\hline
		141 \\
				\hline
		139 \\
				\hline
		138 \\
				\hline
		169 \\
				\hline
	\caption{Time in miliseconds to parse}
	\label{tbl:time_patse}
\end{longtable}