\section*{References}
\label{sec:references}

\bibliography{sqlite_visualiser_report.bib}	

\begin{thebibliography}{0}

% order aphabeticaly by first name.
\bibitem[Antonopoulos, 2014]{bitcoin}
Antonopoulos A. (2014), Mastering Bitcoin: Unlocking Digital Cryptocurrencies, Book, and Online publication, O'Reilly Media, http://chimera.labs.oreilly.com/books/1234000001802/index.html. Last Accessed 29th January 2016.
\\
\bibitem[Sotomayor, 2010]{chibd}
Sotomayor B. (2010), The xdb File Format. On line publication, University of Chicago, http://people.cs.uchicago.edu/\verb|~|borja/chidb/chidb\verb|_|fileformat.pdf. Last Accessed 18th January 2016.
\\
\bibitem[Comer, 1979]{btreepaper}
Comer D. (1979) Towards Computing Surveys. The Ubiquitous B-Tree, Computing Surveys, Vol 11, No. 2. Purdue University, West Lafayette, Indiana, June 1979, pages 121 - 137.
\\
\bibitem[Nilsson and Stråth, 2012]{test_fx}
Nilsson D. and Stråth H. (2012), TestFX, On line publication, https://github.com/TestFX/TestFX. Last Accessed 17th February 2016
\\
\bibitem[Knuth, 1973]{btreeimprpaper}
Knuth E. D. (1973) The Art Of Computer Programming, Volume 3: "Sorting And Searching", Addison-Wesley Publishing Company, Reading, Massachusetts. Pages 473 - 480.
\\
\bibitem[laysakura, 2012]{sqlitefrag}
Laysakura (2012), Visualize SQLite database fragmentation, On Line Publication, https://github.com/laysakura/SQLiteDbVisualizer. Last Accessed 24th January 2016.
\\
\bibitem[Piacentini, 2003]{sqlitebrowser}
Piacentini M. (2003) DB Browser for SQLite, On Line Publication, http://sqlitebrowser.org/. Last Accessed 24th January 2016.
\\
\bibitem[Chirico, 2004]{sqlitetriggers} 
Chirico M. (2004) SQLite Tutorial, On line publication, http://souptonuts.sourceforge.net/readme\verb|_|sqlite\verb|_|tutorial.html. Last Accessed 29th January 2016.
\\
\bibitem[Owens, 2006]{sqlitedefguide} 
Owens M. (2006). The Definitive Guide to SQLite, Berkeley, California, Apress. 
\\
\bibitem[Merkle, 1988]{merkletree}
Merkle R. (1988). "A Digital Signature Based on a Conventional Encryption Function". Advances in Cryptology — CRYPTO '87. Lecture Notes in Computer Science 293. p. 369.
\\
\bibitem[Hipp, 2000]{sqlite} 
Hipp R. (2000) Sqlite. On line publication, Wyrick Company, Inc, https://www.sqlite.org/. Last Accessed 17th January 2016.
\\
\bibitem[Hipp, 2015]{sqlitetalk} 
Hipp R. (2015) SQLite: The Database at the Edge of the Network. On line Video, Skookum, https://www.youtube.com/watch?v=Jib2AmRb\verb|_|rk. Last Accessed 17th January 2016.
\\
\bibitem[Drinkwater, 2011]{sausagefactory}
Drinkwater R. (2011) An analysis of the record structure within SQLite databases, Forensics from the sausage factory, On line publication, http://forensicsfromthesausagefactory.blogspot.com/2011/05/analysis-of-record- \newline structure-within.html, Last Accessed 17th January 2016.
\\
\bibitem[Raymond, 2009]{sqliteray}
Raymond, (2009) SQlite.  On line publication, http://ray.bsdart.org/man/sqlite/. Last Accessed 17th January 2016.

\end{thebibliography}